### 2020-07-16 article.tex
Small note about DtN

    \subsubsection{Extension of the GenEO framework}
The local generalized eigenvalue problems~\cref{eq:gevp} can also be adjusted.
In addition to the local unassembled Neumann matrices~$\{\mathring{A}_i\}_{i=1}^N$,
users can prescribe additional local operators defined on the overlapping subdomain and
with optimized Robin
boundary conditions $\{B_i\}_{i=1}^N$ via
the routine \pk{PCHPDDMSetRHSMat}(pc, $B_i$).
In such a case, the following generalized eigenvalue problems, called GenEO-2 in the
literature~\cite{haferssas2017soras}, are then solved in each subdomain:
\begin{equation*}
    \mathring{A}_i y_i = \lambda_i B_i y_i.
\end{equation*}
This may be useful when dealing with nearly indefinite systems, e.g., nearly incompressible elasticity or the system of Stokes.
Indeed, for such equations, one needs to compute a lot of eigenvectors from the classical GenEO eigenproblem~\cref{eq:gevp} to generate a robust preconditioner. GenEO-2 alleviates this phenomenon.

@@

>>>>

    \subsubsection{Extension of the GenEO framework}
The local generalized eigenvalue problems~\cref{eq:gevp} can also be adjusted.
In addition to the local unassembled Neumann matrices~$\{\mathring{A}_i\}_{i=1}^N$,
users can prescribe additional local operators $\{B_i\}_{i=1}^N$, defined on
the overlapping decomposition, via the routine \pk{PCHPDDMSetRHSMat}(pc, $B_i$).
In the case of local matrices with optimized Robin transmission conditions, the
following generalized eigenvalue problems, called GenEO-2 in the
literature~\cite{haferssas2017soras}, are then solved in each subdomain:
\begin{equation*}
    \mathring{A}_i y_i = \lambda_i B_i y_i.
\end{equation*}
This may be useful when dealing with nearly indefinite systems, e.g., nearly
incompressible elasticity or the system of Stokes. Indeed, for such equations,
one needs to compute a lot of eigenvectors from the classical GenEO
eigenproblem~\cref{eq:gevp} to generate a robust preconditioner. GenEO-2
alleviates this phenomenon. In the case where the local operators
$\{B_i\}_{i=1}^N$ are the discrete mass matrices on the subdomains interfaces,
the so-called Dirichlet-to-Neumann coarse operator is constructed. This has
proven to be efficient for solving the heterogeneous Helmholtz
equation~\cite{conen2014coarse}.

@@

\bibitem{conen2014coarse}
{\sc L.~Conen, V.~Dolean, R.~Krause, and F.~Nataf}, {\em {A coarse space for
  heterogeneous Helmholtz problems based on the Dirichlet-to-Neumann
  operator}}, Journal of Computational and Applied Mathematics, 271 (2014),
  pp.~83--99.
